\documentclass[a4paper,8pt]{extarticle}


\thispagestyle{empty}
\usepackage[compact]{titlesec}
\usepackage{titling}
\usepackage[top=0.34in, left=1in]{geometry}

\titleformat{\section}
{\huge\bfseries\lowercase}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\bfseries\Large}
{\hspace{0.0in}$\bullet$}
{0em}
{}

\titleformat{\subsubsection}[runin]
{\bfseries}
{\hspace{0.0in}}
{0em}
{}[---]

\titlespacing{\subsubsection}
{0em}
{0.25em}
{1em}
\titlespacing{\subsubsubsection}
{0em}
{0.25em}
{1em}


\renewcommand{\maketitle}{
\begin{center}
{\huge\bfseries
\theauthor}
\vspace{0.25em}
\\
	farhansaif488@gmail.com --- https://farhansaif.xyz --- https://github.com/overlorde
\end{center}
}


\begin{document}


\title{R\'esum\'e}

\author{Farhan Saif}

\maketitle

\section{summary}
Aspiring software engineer specializing in backend development with research interest in computer security, more inclined to reverse engineering and malware analysis.

\section{Education}
BSc in Computer Science And Engineering \hspace{6cm} Fall 2019 - Summer 2022\\
Islamic University of Technology\\
Gazipur, Dhaka\\ \\
High School Certificate \hspace{11cm} 2018\\
Notre Dame College\\
Motijheel, Dhaka\\






\section{Technical Skills}
\subsection{Languages }
\subsubsection{Programming}
Python , C/C++ , Javascript/Typescript , Dart , Java
\subsubsection{Scripting}
Bash, Python
\subsubsection{Markup}
HTML, CSS, Markdown, {\LaTeX}
\subsection{Frameworks}
\subsubsection{Web Frontend}
React, Tailwind
\subsubsection{Web Backend}
Flask , NodeJs(Runtime), Express.js, Sequelize, Auth0
\subsubsection{Database}
PostgreSQL, Firebase Cloud Firestore, Mongodb
\subsubsection{Mobile Development}
Flutter
\subsection{Others}
REST API, Git, Github Workflow, Test Automation, Nginx, Server Adminstration.
\section{projects}

\subsection{AutoResuma}
AutoResuma is a web application to generate job-specific Resume for programmers. I developed the REST api for users and implemented jwt authentication. Developed using react, tailwind, chakra and redux in the frontend and nodejs runtime with express.js and postgresql and sequelize in the backend.
\subsection{LifeLine}
LifeLine is an Electronic Health Record application which has blood donation, doctor-patient validation, blood group finder , QR code scanning and many more modules. I worked google maps api integration and user data management implementing blood group finder feature and user profile feature. Developed with flutter framework , cloud firestore and google map api integration.
\subsection{Otris}
Clone of tetris, works cross platform, manupulation of unix terminal commands and multithreading was useful in this case.
\subsection{Jlox-Engine}
A jvm based interpreter for educational language Lox, written in java, used vistitor pattern extensively.
\subsection{Clox-Engine}
An interpreter for educational language lox, which is developed on top of a custom virtual machine which is also written using C.
\subsection{VirgilTex}
A text editor like vim written from scratch using C. Extensive use of unix system calls api and manipulation of unix commands.
\section{Competitions}
\subsection{Capture-The-Flag}
\subsubsection{2021}
26th, National Cyber Drill, 2021
\subsubsection{2021}
10th, IEEE Inter-University CTF, BUET
\subsection{Programming Competition}
\subsubsection{2019}
 12th, Intra-University Programming Competition, IUPC
\end{document}
